---
title: "Fraud"
author: "Jiayi Chen"
date: "9/12/2021"
output: html_document
---
1. change parameters and get a note for how long does it work 
2. record the results (start with iters = 500 and computes AUC curve) 28 financial data; choose one promising year; 
3. write documentations for the rusb and predict.rusb functions


package ebmc 
try them on the data fraud 

1. Read section 1 and 2 on paper
2. 4 slides on Adaboost and RUSBoost

Write own function of NDCG@k 
Understand how nDCG() function in rrecsys package
Read Chapater 8 up to 8.2.3 (skip 8.1.3)


```{r, message=FALSE, warning=FALSE}
library(tidyverse)
library(broom)
library(ISLR)
library(pROC)
#library(StatRank)
```

```{r}
home <- read_csv("uscecchini28.csv")
```

# Preliminary analysis

```{r}
# home %>% 
#   select(fyear, misstate) %>% 
#   filter(fyear == 1990) %>% 
#   summarise(percent = sum(misstate == 1)/n())
# home %>% 
#   select(fyear, misstate) %>%
#   filter(fyear == 2000) %>% 
#   summarise(percent = sum(misstate == 1)/n())
```
# Plot percentage over time 

```{r}
# home2 <- home %>% 
#   select(fyear, misstate) %>%
#   group_by(fyear) %>% 
#   mutate(percent = sum(misstate == 1)/n())
# 
# home2 %>% 
#   ggplot(aes(x = fyear, y = percent)) + 
#   geom_line () +
#   geom_point() +
#   labs(x = "Year", y = "Fraud Percentage") + 
#   ggtitle("Yearly Fraud Percentage over Time") + 
#   theme(plot.title = element_text(hjust = 0.5))

# Passage of the Sarbanes-Oxley Act on July 30, 2002 (Enron Company)
```

# Training set vs test set
```{r}
# smp_size <- floor(0.70 * nrow(home))
# 
# train_ind <- sample(seq_len(nrow(home)), size = smp_size)
# 
# train <- home[train_ind, ]
# test <- home[-train_ind, ]
```

# Split function
```{r}
split_train_test <- function (year, data) {
  train <<- data %>%
    filter(fyear <= year - 2)

  test <<- data %>%
    filter(fyear == year)
}
```

# Logistic evaluation
```{r}
# Use model to make predictions
# write a function takes input test year; split the test and training data
# split_train_test <- function (year) {return two data set}
# for (yr in 2003:2008){split_train_test(year)}
# Fit the logstic model and compute an AUC

result <- c(0)
i = 1

for (yr in 2003:2008){
  split_train_test(yr, home)

  default_model <- glm(formula = misstate ~ act + ap + at + ceq + che + cogs + csho +   dlc + dltis + dltt + ib + invt + ivao + ivst + lct + lt + ppegt + pstk + rect + sale + sstk + txp + prcc_f, data = train, family = "binomial") 
  
  pred_prob <- predict(default_model, newdata = test, type = "response") # predicted probabilities
  pred_class_labels <- ifelse(pred_prob > 0.5, "Yes", "No") # convert to labels
  
roc_obj <- roc(predictor = pred_prob, 
               response = test$misstate)

plot(roc_obj, legacy.axes = TRUE)

result[i] = auc(roc_obj)

i <- i + 1
}

result
```

# FIRST-NDCG@k
```{r First NDCG Function}
NDCG <- function (k, Relevance, Predicted) {
# Calculate DCG@K
  DCGk <- 0
  for (i in 1:k){
    # Assign each observation's relevance value
    rel <- Predicted[i]
    # Sum up DCG values 
    DCGk = DCGk +(2^(rel) - 1)/(log2(i + 1))
  }

# Calculate ideal DCG@K
  iDCGk <- 0
  for (j in 1:k){
    # Similar to the previous for loop, we want to assign each observation's relevance value, except in this case all relevance scores are already ranked from highest to lowest (because it's ideal)
    rel <- Relevance[j]
    iDCGk = iDCGk +(2^(rel) - 1)/(log2(j + 1))
  }
  
  # Print out DCG@k and iDCG@k values
  cat("DCG of the predicted order is", DCGk, "\nDCG of the ideal order(iDCG) is", iDCGk, "\n")
  # Compute NDCG@k
  return(DCGk/iDCGk)
}
```

# SECOND-NDCG@k
```{r Second NDCG Function}
# First, define a function DCG which can calculate the DCG score
DCG <- function (k, ranking){
  DCG <- 0
  for (i in 1:k){
  DCG = DCG +(2^(ranking[i]) - 1)/(log2(i + 1))
  }
  return(DCG)
}

# Then implement the DCG function into the main NDCG function
NDCG2 <- function (k, Relevance, Predicted) {
# Calculate DCG@K
  DCGk <- DCG(k, Predicted)

# Calculate ideal DCG@K
  iDCGk <- DCG(k, Relevance)

  cat("DCG of the predicted order is", DCGk, "\nDCG of the ideal order(iDCG) is", iDCGk, "\n")
  return(DCGk/iDCGk)
}
```

# Apply to the Fraud's data, choosing year 2008 as testset
```{r}
# Adding prediction to a test set
default_model <- glm(formula = misstate ~ act + ap + at + ceq + che + cogs + csho +   dlc + dltis + dltt + ib + invt + ivao + ivst + lct + lt + ppegt + pstk + rect + sale + sstk + txp + prcc_f, data = train, family = "binomial") 

# In this case, k = the number of top 1% firms in a test year
k <- floor(0.01*nrow(test))

# Ideal order
RelevanceLevel <- sort(test$misstate, decreasing = TRUE)

# Recommendations order
testpred <- test %>% 
    mutate(pred = pred_prob <- predict(default_model, newdata = test, type = "response")) %>%
    arrange(desc(pred))
PredictedRank <- testpred$misstate

NDCG(k, RelevanceLevel, PredictedRank)
NDCG2(k, RelevanceLevel, PredictedRank)

# The logit method's NDCG@k value from the paper is 0.028
```


# Logistic 

*act -- Current Assets, Total
*ap -- Account Payable, Trade
*at -- Assets, Total
*ceq - -Common/Ordinary Equity, Total
*che -- Cash and Short-Term Investments
*cogs -- Cost of Goods Sold
*csho -- Common Shares Outstanding
*dlc -- Debt in Current Liabilities, Total
*dltis -- Long-Term Debt Issuance
*dltt -- Long-Term Debt, Total
dp -- Depreciation and Amortization
*ib -- Income Before Extraordinary Items
*invt -- Inventories, Total
*ivao -- Investment and Advances, Other
*ivst -- Short-Term Investments, Total
*lct -- Current Liabilities, Total
*lt -- Liabilities, Total
ni -- Net Income (Loss)
*ppegt -- Property, Plant and Equipment, Total
*pstk -- Preferred/Preference Stock (Capital), Total
re -- Retained Earnings
*rect -- Receivables, Total
*sale -- Sales/Turnover (Net)
*sstk -- Sale of Common and Preferred Stock
*txp -- Income Taxes Payable
txt -- Income Taxes, Total
xint -- Interest and Related Expense, Total
*prcc_f -- Price Close, Annual, Fiscal

dch_wc -- WC accruals
ch_rsst -- RSST accruals
dch_rec -- Change in receivables
dch_inv -- Change in inventory
soft_assset -- % Soft assets
dpi -- Depreciation index
ch_cs -- Change in cash sales
ch_cm -- Change in cash margin
ch_roa -- Change in return on assets
ch_fcf -- Change in free cash flows
reoa -- Retained earnings over total assets
EBIT -- Earnings before interest and taxes over total assets
issue -- Actual issuance
bm -- Book-to-market

$log(p/(1-p)) = intercept + slope1*exp1 + slope2*exp2 + ... + slopeP*expP$