```{r message=FALSE, warning=FALSE}
#setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
library(tidyverse)
library(rusboost)
library(rpart)
suppressPackageStartupMessages(library(ISLR))
suppressPackageStartupMessages(library(pROC))
#library(rattle)
#library(ebmc)
#Package ‘ebmc’ was removed from the CRAN repository.
#Archived on 2021-03-16 as requires archived package 'DMwR'
```

```{r, message=FALSE}
load("C:/Users/cjy2001/OneDrive - Middlebury College/Middlebury Academic/Fall 2021/Project/11.4.RData")
data <- read_csv("uscecchini28.csv")
data$misstate <- factor(data$misstate)
```

```{r Creating data}
split_train_test <- function (year, data) {
  train <<- data %>%
    filter(fyear <= year - 2)
  test <<- data %>%
    filter(fyear == year)
}

split_train_test(2003, data)
train_3 <- train
test_3 <- test
split_train_test(2004, data)
train_4 <- train
test_4 <- test
split_train_test(2005, data)
train_5 <- train
test_5 <- test
split_train_test(2006, data)
train_6 <- train
test_6 <- test
split_train_test(2007, data)
train_7 <- train
test_7 <- test
split_train_test(2008, data)
train_8 <- train
test_8 <- test
# How to rename them by using for loop?
# Importance of dealing with serial fraud in fraud prediction models.
# The value of model6 is too strange (too many predicted fraud)
# Error: cannot allocate vector of size 1.3 Gb
```

We find that our best model, the ensemble learning model, identified a total of 16 fraud cases in the test period 2003–2008. In contrast, the comparable figure is 9 for the Dechow et al. model and 7 for the Cecchini et al. model. These results suggest that the differences in the performance of the ensemble learning model versus the two benchmark models are also economically significant.

p.207: We construct our RUSBoost model by setting this ratio at 1:1. That is, we simply sample the same number of fraud observations and non-fraudulent observations.\
p.223: We set the number of trees to 3,000.\
p.223: We set the parameter “minleaf” (minimum required number of samples at a tree leaf) to 5.


```{r}
set.seed(5)
#.Random.seed  Check seed is the same
year4_time_3000 <- system.time(year4_model_3000 <- rusb(formula = misstate ~ act + ap + at + ceq + che + cogs + csho + dlc + dltis + dltt + dp
              + ib + invt + ivao + ivst + lct + lt + ni + ppegt + pstk + + re + rect + sale + sstk + txp + txt + xint + 
                prcc_f,
              data = train_4,
              boot = FALSE,
              iters = 3000, 
              control = rpart.control(minsplit = 5),
              sampleFraction = 0.5,
              idx = train_4$misstate == 0)
)

year5_time_3000 <- system.time(year5_model_3000 <- rusb(formula = misstate ~ act + ap + at + ceq + che + cogs + csho + dlc + dltis + dltt + dp
              + ib + invt + ivao + ivst + lct + lt + ni + ppegt + pstk + + re + rect + sale + sstk + txp + txt + xint + 
                prcc_f,
              data = train_5,
              boot = FALSE,
              iters = 3000, 
              control = rpart.control(minsplit = 5),
              sampleFraction = 0.5,
              idx = train_5$misstate == 0)
)

year6_time_3000 <- system.time(year6_model_3000 <- rusb(formula = misstate ~ act + ap + at + ceq + che + cogs + csho + dlc + dltis + dltt + dp
              + ib + invt + ivao + ivst + lct + lt + ni + ppegt + pstk + + re + rect + sale + sstk + txp + txt + xint + 
                prcc_f,
              data = train_6,
              boot = FALSE,
              iters = 3000, 
              control = rpart.control(minsplit = 5),
              sampleFraction = 0.5,
              idx = train_6$misstate == 0)
)
```

```{r,eval=FALSE}
# These are all for year 2003.
set.seed(5)

time_5000 <- system.time(model_5000 <- rusb(formula = misstate ~ act + ap + at + ceq + che + cogs + csho + dlc + dltis + dltt + dp
              + ib + invt + ivao + ivst + lct + lt + ni + ppegt + pstk + + re + rect + sale + sstk + txp + txt + xint + 
                prcc_f,
              data = train_3,
              boot = FALSE,
              iters = 5000, 
              control = rpart.control(minsplit = 5),
              sampleFraction = 0.5,
              idx = train_3$misstate == 0)
)

time_3000 <- system.time(model_3000 <- rusb(formula = misstate ~ act + ap + at + ceq + che + cogs + csho + dlc + dltis + dltt + dp
              + ib + invt + ivao + ivst + lct + lt + ni + ppegt + pstk + + re + rect + sale + sstk + txp + txt + xint + 
                prcc_f,
              data = train,
              boot = FALSE,
              iters = 3000, 
              control = rpart.control(minsplit = 5),
              sampleFraction = 0.5,
              idx = train$misstate == 0)
)

time_1500 <- system.time(model_1500 <- rusb(formula = misstate ~ act + ap + at + ceq + che + cogs + csho + dlc + dltis + dltt + dp
              + ib + invt + ivao + ivst + lct + lt + ni + ppegt + pstk + + re + rect + sale + sstk + txp + txt + xint + 
                prcc_f,
              data = train,
              boot = FALSE,
              iters = 1500, 
              control = rpart.control(minsplit = 5),
              sampleFraction = 0.5,
              idx = train$misstate == 0)
)

time_500 <- system.time(model_500 <- rusb(formula = misstate ~ act + ap + at + ceq + che + cogs + csho + dlc + dltis + dltt + dp
              + ib + invt + ivao + ivst + lct + lt + ni + ppegt + pstk + + re + rect + sale + sstk + txp + txt + xint + 
                prcc_f,
              data = train,
              boot = FALSE,
              iters = 500, 
              control = rpart.control(minsplit = 5),
              sampleFraction = 0.5,
              idx = train$misstate == 0)
)

time_200 <- system.time(model_200 <- rusb(formula = misstate ~ act + ap + at + ceq + che + cogs + csho + dlc + dltis + dltt + dp
              + ib + invt + ivao + ivst + lct + lt + ni + ppegt + pstk + + re + rect + sale + sstk + txp + txt + xint + 
                prcc_f,
              data = train,
              boot = FALSE,
              iters = 200, 
              control = rpart.control(minsplit = 5),
              sampleFraction = 0.5,
              idx = train$misstate == 0)
)
```

model_100 takes 800 seconds\
model_200 takes 1650/1800 seconds\
model_500 takes 3200/3600 seconds\
model_1500 takes 7500/7000 seconds\
model_3000 takes 17000 seconds\
year4_model_3000 takes 15000 seconds\
year5_model_3000 takes 15000 seconds\
year6_model_3000 takes 2700 seconds??\

```{r Prediction, eval=FALSE}
preds_100 <- predict.rusb(year3_model_100, data.frame(test_3))
preds_200 <- predict.rusb(model_200, data.frame(test))
preds_500 <- predict.rusb(model_500, data.frame(test))
preds_1500 <- predict.rusb(model_1500, data.frame(test))
preds_3000 <- predict.rusb(model_3000, data.frame(test))
```

```{r AUC}
auc <- NULL
x <- list(preds_200, preds_500, preds_1500, preds_3000)

for (i in 1:4){
roc_obj <- roc(predictor = x[[i]]$prob[,2], 
               response = test$misstate)

#plot(roc_obj, legacy.axes = TRUE)
auc[i] = auc(roc_obj)
}

auc
```

```{r Confusion Sensitivity Precision}
# Sensitivity TP/P = TP/(TP + FN) 
# Precision TP/TP+FP
sensitivity <- NULL
precision <- NULL

for (i in 1:4) {
  print(x[[i]]$confusion)
  sensitivity[i] <- x[[i]]$confusion[2,2]/sum(x[[i]]$confusion[,2])
  precision[i] <- x[[i]]$confusion[2,2]/sum(x[[i]]$confusion[2,])
}

sensitivity
precision
```

```{r}
year3_preds_3000 <- predict.rusb(year3_model_3000, data.frame(test_3))
year4_preds_3000 <- predict.rusb(year4_model_3000, data.frame(test_4))
year5_preds_3000 <- predict.rusb(year5_model_3000, data.frame(test_5))
year6_preds_3000 <- predict.rusb(year6_model_3000, data.frame(test_6))

yearly_test_set <- list(test_3,test_4,test_5,test_6)
yearly_preds <- list(year3_preds_3000,year4_preds_3000,year5_preds_3000,year6_preds_3000)
yearly_sensitivity <- NULL
yearly_precision <- NULL
yearly_auc <- NULL

for (i in 1:4) {
  roc_obj <- roc(predictor = yearly_preds[[i]]$prob[,2], 
               response = yearly_test_set[[i]]$misstate)
  print(yearly_preds[[i]]$confusion)
  yearly_sensitivity[i] <-
    yearly_preds[[i]]$confusion[2,2]/sum(yearly_preds[[i]]$confusion[,2])
  yearly_precision[i] <- yearly_preds[[i]]$confusion[2,2]/sum(yearly_preds[[i]]$confusion[2,])
  yearly_auc[i] = auc(roc_obj)
}
mean(yearly_auc)
mean(yearly_precision)
mean(yearly_sensitivity)
```

```{r}
set.seed(5)
year6_time_3000_2 <- system.time(year6_model_3000_2 <- rusb(formula = misstate ~ act + ap + at + ceq + che + cogs + csho + dlc + dltis + dltt + dp
              + ib + invt + ivao + ivst + lct + lt + ni + ppegt + pstk + + re + rect + sale + sstk + txp + txt + xint + 
                prcc_f,
              data = train_6,
              boot = FALSE,
              iters = 3000, 
              control = rpart.control(minsplit = 5),
              sampleFraction = 0.5,
              idx = train_6$misstate == 0)
)
```

```{r}
test_8 %>% 
  count(misstate == 1)
test_7 %>% 
  count(misstate == 1)
test_6 %>% 
  count(misstate == 1)
test_5 %>% 
  count(misstate == 1)
test_4 %>% 
  count(misstate == 1)
```



